\textsf{Are large language models superhuman chemists?}

### 2024-03-24 src/tex/ms.tex
more updates

\paragraph{Study design}
For our initial study we wanted to maximize the response rate given our available resources. 
For this reason, we did not opt for a highly controlled study setting. 
That is, while users were prompted to not use external tools other than a calculator and to not consult other humans, we do not have any way to verify that the participants complied with those rules. 
Note that users were also allowed to skip questions.

Another aspect of requiring unsupervised question answering is that in the real world humans also have tools and are able to use them for answering any question of interest.

\paragraph{Participants}
Users were open to report about their experience in chemistry. 
Overall, \variable{output/num_users_with_education_info.txt} did so. 
Out of those, \variable{output/num_human_phd.txt} reported to have been awarded a Ph.D.
\variable{output/num_human_postdoc.txt} are beyond a first postdoc, \variable{output/num_human_master.txt} have a master's degree, and \variable{output/num_human_bachelor.txt} have a bachelor's degree.

>>>>

\paragraph{Study design}
For our initial study we wanted to maximize the response rate given our available resources. 
For this reason, we did not opt for a highly controlled study setting. 
That is, while users were prompted to not use external tools other than a calculator and to not consult other humans, we do not have any way to verify that the participants complied with those rules (note that users were also allowed to skip questions). Another aspect of requiring unsupervised question answering is the real world equivalent of our benchmark, where humans have unencumbered access to tools and are able to answer any question of interest.

\paragraph{Participants}
Users were open to report about their experience in chemistry. 
Overall, \variable{output/num_users_with_education_info.txt} did so. 
Out of those, \variable{output/num_human_phd.txt} reported to have been awarded a doctoral degree.
\variable{output/num_human_postdoc.txt} are beyond a first postdoctorate, \variable{output/num_human_master.txt} have a master's degree, and \variable{output/num_human_bachelor.txt} have a bachelor's degree.
